### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:18	18:42:05	(Tue18.Mar)

\ai{Thank you, crude grammar correction applied.}

@@

\ai{We agree that this should should be clarified, and }

@@

\newpage
\section{Answer to reviewer 2}

@@

\ans{We thank the reviewer for these remarks, it seems we should state this better upfront. In the 5th paragraph of the introduction we now explain that our system is a well sampled wideband sonar.}

@@

\ai{The reviewer made us realize that this was not clear enough in the article. The 32 elements are evenly spaced along the 1.2m array, so:

@@

\ai{Appreciations for pointing this out. We agree that this should be clarified. The array configuration produce the first grating lobes at $\theta = \text{arcsin}(\lambda M/D) = 23.5^\circ$, but this is not a problem since the element opening angle is $25^\circ$ ($\theta\in[12.5^\circ,12.5^\circ]$) at $f_c=100$\;kHz. In the paper we addition we perform sidescan imaging where only very narrow beams need to be beamformed. These details are now included in the paper, some in the 5th paragraph of the introduction and some in the first paragraph of section IV.}

@@

\ai{Yes, we are pre-steering the array for every angle. We have clarified this further (see 3.), and added a remark saying that while not necessary here we could have phase steered the array by introducing the steering vector $\vec s$.}

@@

\begin{enumerate}
\qi{It is unfortunate that so little effort was made to speed up the CPU versions of the code. For example, there are public-domain versions of optimized LAPACK libraries that provide the same sort of linear algebra codes as the authors used in their CPU implementation (for example, GoToBLAS, or Intel's MKL libraries).}
\ai{We agree, and have now included our reasons for not comparing with an optimized CPU implementation.  One reason is that we have not been able to find any CPU batch solvers out there and lacked the time to make our own. In our tests our custom inline Cholesky solver beat alternatives from e.g. MKL as our matrices are too small to justify the extra function call overhead. Another reason is that to make the comparison fair we feel an equal effort would have to put into writing a covariance builder for the CPU, and to minimize data movement in each step and in between them. The details may be found in section V paragraph 2.}
%
\qi{The extra input/output of data to the GPU is a burden only on the GPU implementation, so would penalize the GPU implementation only, unless the authors were to "hide" the i/o by setting it up to run in parallel with the CPU processing, which is easier and easier with the latest GPU architectures. This should perhaps be pointed out.}
\ai{Yes this is a good point. Included in last paragraph of section IV.}
%
\qi{The authors do not provide much information about the GPU hardware they used, the NVIDIA Quadro 6000. How does this compare to the desktop video cards that reside in most desktop, workstation, server and even high-end laptop systems? What is the vintage of the architecture of this GPU? How has the architecture evolved? For example, the authors tell us the Quadro 6000 (\$1900, 6GB VRAM, 448 cores) is a Fermi architecture - this is the previous architecture, having been superceded by the Kepler architecture, with a new Quadro K6000 board (\$3600, 12 GB VRAM, 2880 cores). The Quadro boards are high-end boards with video output targeting the CADAM market - there are many cheaper alternatives targeted at gamers and an even more expensive compute-only board called TESLA targeted at high performance computing. It's difficult to say how much of this irrelevant.}
\ai{There is certainly a potential for comparing with many other cards here, but we decided to be thorough with one architecture than to compare with everything. To the paragraph introducing the Quadro 6000 we have explained what its equivalent consumer grade Geforce card would be. We have also included remarks that we expect Kepler to perform better had the design been optimized for it.}
%
\qi{The authors state that OpenCL is an equally attractive alternative to CUDA. This would be the case if the authors had been able to find something in OpenCL akin to the recently released batch-optimized linear solver code for CUDA. Unfortunately, this is a pervasive story - the support for scientific programming in CUDA is years ahead of OpenCL. The benefit of OpenCL is that it is supposed to be "cross-platform", which is true in theory, but it is hard to imagine being true in practice considering the wide range of heterogeneous computing elements OpenCL is supposed to cover; from phones to DSP chips to FPGAs. }
\ai{These are important remarks, thank you. We have written OpenCL programs too, and run them on Intel CPUs and GPUs from AMD and Nvidia. It was no walk in the park, but with a satisfactory end result. But like you say, these are just a subset of devices that OpenCL support, and we have now changed the wording to be more specific here. Your remark on the lack a batched linear solver is spot in, the sentence is now rewritten.}
\end{enumerate}

@@

\ans{The reviewer is absolutely right. The copy will be serialized due to divergent branching. It is unfortunate that no Cholesky based batch linear equation solver exist, which would have eliminated the need for the lower triangular... The paragraph has been edited to explain this better.}

>>>>

\ai{Crude grammar correction applied.}

@@

\ai{We agree that this should should be clarified, but since the transfer can happen in parallel without adding to the computation time we do not believe this point belongs in the introduction. An elaboration on the topic is included in the last paragraph in section IV. }

@@

\section{Answer to reviewer 2}

@@

\ans{We thank the reviewer for these remarks, it seems we should state this better upfront. In the 5th paragraph of the introduction we now explain that our system is a well sampled wideband sonar and that we operate in near field conditions.}

@@

\ai{The reviewer made us realize that we should clarify this. The 32 elements are evenly spaced along the 1.2m array, so:

@@

\ai{Appreciations for pointing this out. We agree that this should be clarified. The array configuration produce the first grating lobes at $\theta = \text{arcsin}(\lambda M/D) = 23.5^\circ$, but this is not a problem since the element opening angle is $25^\circ$ ($\theta\in[12.5^\circ,12.5^\circ]$) at $f_c=100$\;kHz. In the paper we perform sidescan imaging where only very narrow beams need to be beamformed. These details are now included in the paper, some in the 5th paragraph of the introduction and some in the first paragraph of section IV.}

@@

\ai{Yes, we are pre-steering the array for every angle. We have clarified this further (see 3.), and added a remark saying that while we can not use it here (due to processing a wideband signal) a phase steered version of MVDR can be obtained by introducing a steering vector $\vec s$.}

@@

\begin{enumerate}
\qi{It is unfortunate that so little effort was made to speed up the CPU versions of the code. For example, there are public-domain versions of optimized LAPACK libraries that provide the same sort of linear algebra codes as the authors used in their CPU implementation (for example, GoToBLAS, or Intel's MKL libraries).}
\ai{We agree, and have now included our reasons for not comparing with an optimized CPU implementation.  One reason is that we have not been able to find any CPU batch solvers out there and lacked the time to make our own. In our tests our custom inline Cholesky solver beat alternatives from e.g. MKL as our matrices are too small to justify the extra function call overhead. Another reason is that to make the comparison fair we feel an equal effort would have to put into writing a covariance builder for the CPU, and to minimize data movement in each step and in between them. The details may be found in section V paragraph 2.}
%
\qi{The extra input/output of data to the GPU is a burden only on the GPU implementation, so would penalize the GPU implementation only, unless the authors were to "hide" the i/o by setting it up to run in parallel with the CPU processing, which is easier and easier with the latest GPU architectures. This should perhaps be pointed out.}
\ai{Yes this is a good point. Included in last paragraph of section IV.}
%
\qi{The authors do not provide much information about the GPU hardware they used, the NVIDIA Quadro 6000. How does this compare to the desktop video cards that reside in most desktop, workstation, server and even high-end laptop systems? What is the vintage of the architecture of this GPU? How has the architecture evolved? For example, the authors tell us the Quadro 6000 (\$1900, 6GB VRAM, 448 cores) is a Fermi architecture - this is the previous architecture, having been superceded by the Kepler architecture, with a new Quadro K6000 board (\$3600, 12 GB VRAM, 2880 cores). The Quadro boards are high-end boards with video output targeting the CADAM market - there are many cheaper alternatives targeted at gamers and an even more expensive compute-only board called TESLA targeted at high performance computing. It's difficult to say how much of this irrelevant.}
\ai{There is certainly a potential for comparing with many other cards here, but we decided to be thorough with one architecture rather than to compare with everything. To the paragraph introducing the Quadro 6000 we have explained what its equivalent consumer grade Geforce card would be. We have also included remarks that we expect Kepler to perform better had the design been optimized for it.}
%
\qi{The authors state that OpenCL is an equally attractive alternative to CUDA. This would be the case if the authors had been able to find something in OpenCL akin to the recently released batch-optimized linear solver code for CUDA. Unfortunately, this is a pervasive story - the support for scientific programming in CUDA is years ahead of OpenCL. The benefit of OpenCL is that it is supposed to be "cross-platform", which is true in theory, but it is hard to imagine being true in practice considering the wide range of heterogeneous computing elements OpenCL is supposed to cover; from phones to DSP chips to FPGAs. }
\ai{These are important remarks, thank you. We have written OpenCL programs too, and run them on Intel CPUs and GPUs from AMD and Nvidia. It was no walk in the park, but with a satisfactory end result. But like you say, these are just a subset of devices that OpenCL support, and we have now changed the wording to be more specific here. Your remark on the lack a batched linear solver is spot in, the sentence is now rewritten.}
\end{enumerate}

@@

\ans{The reviewer is absolutely right. The copy will be serialized due to divergent branching. It is unfortunate that to the best of our knowledge no Cholesky based batch linear equation solver exist, which would have eliminated the need for the lower triangular... The paragraph has been edited to explain this better.}
